Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd
update

Univariate regression
analysis results exploring the association between the exposures,
selected potential confounding variables showed substantial associations between BMI ($\beta = 0.95$ mmHg; 95%CI [0.60 - 1.3]; p<0.05), TC ($\beta = 3.6$ mmHg; 95%CI [2.9 - 4.3]; p<0.05), albumin ($\beta = -0.48$ mmHg; 95% CI [-0.68mmHg - -0.27]; p < 0.05), AST ($\beta = 0.12$ mmHg; 95%CI [0.07 - 0.18]; p <0.05), and age (years) ($\beta = 0.49$ mmHg; 95% CI [0.45 - 0.52]; p <0.05) and systolic blood pressure. Weekday sleep duration between 6 and 8 hours was associated with a 4.0 mmHg (95% CI [-6.8 - -1.2]) decrease in the average systolic blood pressure compared to 6 hours of sleep. On the other hand, more than 8 hours of sleep was associated with a decrease of 3.1 mmHg in systolic blood compared to 6 hours of sleep. Substantial associations were noted between citizenship, education, number of children below five years, gender, marital status, race, smoking status, snorting, alcohol, and income.

```{r tabthree, echo=FALSE, eval=FALSE}
## univariate analysis
sbp.univariate %>% 
  as_kable_extra(format = "latex", booktabs = TRUE, digits = 2, caption = "Univariate analyses of exposures, potential confounding factors and systolic blood pressure. BMI = Body Mass Index; HDL = High Density Lipoprotein, TC = Total Cholestrol level; AST = aspertate aminotransferase.", longtable = TRUE)
```

>>>>

Table \@ref(tab:tabthree) presents the summary of univariate regression
analysis results exploring the association between the exposures,
selected potential confounding variables and systolic blood pressure. We
found substantial associations between ...

```{r tabthree, echo=FALSE}
## univariate analysis
sbp.univariate %>% 
  as_kable_extra(format = "latex", booktabs = TRUE, digits = 2, caption = "Univariate analyses of exposures, potential confounding factors and systolic blood pressure. BMI = Body Mass Index; HDL = High Density Lipoprotein, TC = Total Cholestrol level; AST = aspertate aminotransferase.", longtable = TRUE)
```
